---
title: "Using Association Rules Mining to Characterize of Loss of Control Eating in Childhood"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
  html_document: default
header-includes:
- \usepackage{fullpage}
- \usepackage{graphicx}
- \usepackage{subcaption}
- \usepackage{float}
- \usepackage{placeins}
- \usepackage{caption}
- \usepackage{mathtools}
- \usepackage{rotating}
- \usepackage{multirow}
- \usepackage{amssymb}
- \usepackage{amsmath}
- \usepackage{bigstrut}
- \usepackage{geometry}
- \usepackage{longtable}
- \usepackage{rotating}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE, tidy.opts = list(comment = FALSE), echo = TRUE, fig.width=6, fig.height=4, fig.path='LOC_figs/', echo=FALSE, warning=FALSE, message=FALSE, comment = NA)
```


<!-- load startup file and any extra packages -->
```{r load_packages, echo=FALSE, include=FALSE}
library(knitr)
library(kableExtra)
```
<!-- The number of hashtags (#) will determine the boldness of heading -->

\clearpage

# Descriptive Statistics

## Demographic Characteristics

```{r load_descriptive, echo=FALSE, include=FALSE}
source('LOC_Descriptive.R')
```

Children with LOC-eating (N=37, 25%) and with no LOC-eating (N=112, 75%) did not differ by age, ethnicity, or socio-economic status as assessed by income and parental education (p’s > 0.105; Table 1). However, children who reported LOC-eating had higher BMI-for-age percentile (t(65) = -2.56, p = 0.013; d = 0.47) despite not differing from those who did not report LOC-eating when weight status was tested as a categorical variable ($\chi^2$ = 3.83, p = 0.147). Additionally, there was trend for different racial distributions such that the sample of children who reported LOC-eating was slightly more diverse than the sample of those who did not report LOC-eating (Table 1). 

### Table 1

\begin{table}[ht!]
\centering
\begin{tabular}{lcl@{\hspace{5pt}}cc}
  \hline
  & \multicolumn{1}{c}{Full Sample} && \multicolumn{2}{c}{LOC}\bigstrut[t] \\
  & && \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{No} \bigstrut[t] \\
  \cline{2-2} \cline{4-5}
  Total\scriptsize{(\textit{N} (Male))}    & 177 (91)  && 37 (19)  & 121 (63)  \\
  \hspace{10pt} LOC Not Reported        & 19  &&  &    \\
  Age\scriptsize{(Mean (SD))}& 9.19 (1.32)  && 8.89 (1.31) &  9.28 (1.37)   \\
  BMI percentile\scriptsize{(Mean (SD))} & 60.02 (28.48)  && 71.49 (26.24) &  57.64 (27.64)   \\
  BMI Status\scriptsize{(\textit{N} (\%))} &   &&  &     \\
  \hspace{10pt} Obese                   & 23 (13\%)  && 8 (22\%) & 13 (11\%)   \\
  \hspace{10pt} Overweight              & 24 (14\%)  && 7 (19\%) & 14 (12\%) \\
  \hspace{10pt} Healthy Weight          & 128 (72\%) && 22 (59\%) & 93 (77\%)   \\
  \hspace{10pt} Underweight             & 2  (1\%)  && 0  & 1 (<1\%)  \\
  Ethnicity\scriptsize{(\textit{N} (\%))}&   &&  &    \\
  \hspace{10pt} Hispanic/Latino     & 8 (5\%)  && 2 (2\%)  & 5 (4\%)   \\
  \hspace{10pt} Not Hispanic/Latino & 126 (71\%) && 33 (89\%)  & 76 (63\%)  \\
  \hspace{10pt} Not Reported        & 42 (24\%) && 2 (5\%)   & 34 (28\%) \\
  Race$^{A}$\scriptsize{(\textit{N} (\%))}&   &&  &    \\
  \hspace{10pt} Black/African American & 6 (3\%)  && 4 (11\%) & 2 2\% \\
  \hspace{10pt} White                  & 161 (91\%) && 31 (84\%) & 114 (94\%) \\
  \hspace{10pt} Other                  & 8 (5\%)  && 1 (3\%)  & 4 (3\%)   \\
  \hspace{10pt} Not Reported           & 2 (1\%)   && 1 (3\%) & 1 (<1\%)  \\
  \hline
  \multicolumn{5}{l}{BMI: body mass index; LOC: loss of control} \\
  \multicolumn{5}{l}{Children with and without LOC were compared using independent samples } \\
  \multicolumn{5}{l}{t-tests, chi2 or Fisher tests as appropriate.} \\
  \multicolumn{5}{l}{Note: percentages were rounded to nearest whole number so columns may } \\
  \multicolumn{5}{l}{not add to 100\% due to rounding error.} \\
\end{tabular}
\end{table}

\FloatBarrier

## Family and Early Life Characteristics. 

Children who reported LOC-eating did not differ on average from those with no LOC-eating for reported breastfeeding duration, parental education, income, or parental weight status (Table 2). For both groups, the majority of children were breastfed for at least 4 months, had parents with education that went beyond high school, and had yearly family income of at least $50,000. Overall, a greater proportion of fathers met criteria for overweight or obesity (66%) than mothers (35.6%).   

### Table 2

\begin{table}[ht!]
\centering
\begin{tabular}{lcl@{\hspace{5pt}}cc}
  \hline
  & \multicolumn{1}{c}{Full Sample} && \multicolumn{2}{c}{LOC}\bigstrut[t] \\

  & && \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{No} \bigstrut[t] \\
  \cline{2-2} \cline{4-5}
  Breast Fed Duration\scriptsize{(\textit{N} (\%))}         &   &&  &   \\
  \hspace{10pt} 10+ months & 18 (11\%) && 5 (14\%) & 11 (9\%) \\
  \hspace{10pt} 7-9 months & 36 (21\%)&& 5 (14\%) & 31 (26\%)  \\
  \hspace{10pt} 4-6 months & 51 (30\%) && 13 (35\%) & 35 (29\%) \\
  \hspace{10pt} 1-3 months & 15 (9\%) && 3 (8\%) & 12 (10\%)  \\
  \hspace{10pt} Never      & 53 (31\%) && 10 (27\%) & 30 (25\%)  \\
  \hspace{10pt} Not Reported & 4 (2\%) && 1 (3\%) & 2 (2\%)\\
  Maternal Ed$^{A}$\scriptsize{(\textit{N} (\%))}&   &&  &     \\
  \hspace{10pt} High School          & 26 (15\%)&& 10 (27\%)& 11 (9\%)  \\
  \hspace{10pt} Post High School     & 145 (82\%)&& 26 (70\%)& 105 (87\%) \\
  \hspace{10pt} Not Reported         & 6 (3\%)  && 1 (3\%) & 5 (4\%)  \\  
  Paternal Ed\scriptsize{(\textit{N} (\%))}&   &&  &     \\
  \hspace{10pt} High School          & 37 (21\%) && 9 (24\%) & 22 (18\%)  \\
  \hspace{10pt} Post High School     & 129 (73\%) && 25 (68\%) & 92 (76\%) \\
  \hspace{10pt} Not Reported         & 11 (6\%)  && 3 (1\%) & 7 (6\%)  \\
  SES\scriptsize{(\textit{N} (\%))}         &   &&  &   \\
  \hspace{10pt} $>\$100,000$         & 49 (28\%) && 6 (16\%) & 40 (33\%)  \\
  \hspace{10pt} $\$50,000-\$100,000$ & 83 (47\%) && 21 (57\%) & 54 (45\%) \\
  \hspace{10pt} $<\$50,000$          & 40 (23\%) && 10 (27\%) & 24 (20\%) \\
  \hspace{10pt} Not Reported         & 5 (3\%) && 0  &  3 (2\%) \\
  Maternal BMI Status\scriptsize{(\textit{N} (\%))}&   &&  &      \\
  \hspace{10pt} Class II+ Obesity (BMI > 35) & 20 (11\%)  && 8 (22\%) & 11 (9\%)   \\
  \hspace{10pt} Class I Obesity         & 18 (10\%) && 4 (11\%) & 13 (13\%)   \\
  \hspace{10pt} Overweight              & 25 (14\%) && 5 (14\%) & 19 (16\%)\\
  \hspace{10pt} Healthy Weight          & 75 (42\%) && 15 (41\%) & 57 (47\%)  \\
  \hspace{10pt} Underweight             & 4 (2\%)  && 2 (5\%) & 2 (2\%)  \\
  \hspace{10pt} Not Reported            & 35 (20\%)  && 3 (8\%)  & 19 (16\%)  \\
  Paternal BMI Status\scriptsize{(\textit{N} (\%))}&   &&  &     \\
  \hspace{10pt} Class II+ Obesity (BMI > 35) & 21 (12\%)  && 5 (14\%)  & 12 (10\%)   \\
  \hspace{10pt} Class I Obesity         & 30 (17\%)  && 7 (19\%) & 22 (18\%)   \\
  \hspace{10pt} Overweight              & 66 (37\%)  && 15 (41\%) & 46 (38\%)\\
  \hspace{10pt} Healthy Weight          & 51 (29\%) && 9 (24\%)& 34 (28\%)  \\
  \hspace{10pt} Underweight             & 0   && 0  & 0   \\
  \hspace{10pt} Not Reported            & 9 (5\%)  && 1 (3\%) & 7 (6\%)  \\[1pt]
  \hline
  \multicolumn{5}{l}{BMI: body mass index; LOC: loss of control} \\
  \multicolumn{5}{l}{Children who reported or did not report LOC were compared using independent } \\
  \multicolumn{5}{l}{samples t-tests, chi2 or Fisher tests as appropriate. Note, percentages were} \\
  \multicolumn{5}{l}{rounded to nearest whole number so columns may not add to 100\% due to} \\
  \multicolumn{5}{l}{rounding error} \\
\end{tabular}
\end{table}
\FloatBarrier


## Appetitive Traits

Parents reported significantly lower satiety responsiveness (t(53) = -2.42, p = 0.019) and greater food responsiveness (t(48) = 2.07, p = 0.044) for children who reported LOC-eating than those who did not (Table 3). The groups did not differ on average for any of the other CEBQ scales (p’s > 0.05; Table 3).

\FloatBarrier

### Table 3

\begin{table}[ht!]
\centering
\begin{tabular}{lrl@{\hspace{5pt}}rl@{\hspace{5pt}}rr}
  \hline
  & \multicolumn{6}{c}{Child Eating Behavior Questionnaire} \\
  & \multicolumn{1}{c}{Yes} && \multicolumn{1}{c}{No} && & \bigstrut[t] \\
  \cline{2-2} \cline{4-4}
  & \multicolumn{1}{c}{Mean (SD)} && \multicolumn{1}{c}{Mean (SD)}  && \multicolumn{1}{c}{$d^{a}$} & \multicolumn{1}{c}{$p^{b}$} \bigstrut[t] \\
  \hline
  CEBQ-FR & 2.78 (0.88)  && 2.46 (0.63) && 0.46 & 0.044\\
  CEBQ-EOE  & 2.20 (0.75) && 2.10 (0.61) && 0.15  & 0.478\\
  CEBQ-EF & 3.90 (0.63) && 3.74 (0.67)  && 0.25 & 0.178 \\
  CEBQ-DD & 2.73 (1.09) && 2.55 (0.84)  && 0.20  & 0.350\\
  CEBQ-SR &  2.63 (0.67) && 2.92 (0.57) && 0.49 & 0.019*\\
  CEBQ-SE &  2.59 (0.87)  && 2.75 (0.68)  && 0.19 & 0.310 \\
  CEBQ-EUE & 2.48 (0.64)  && 2.68 (0.84) && 0.25 & 0.129 \\
  CEBQ-FF  & 3.08 (1.0)  && 2.77 (0.84)  && 0.35 & 0.099$^{\dagger}$ \\
  & \multicolumn{6}{c}{Child Feeding Questionnaire} \\
  CFQ-PR  & 4 (0.74)  && 4.02 (0.68)  && 0.02 & 0.910 \\
  CFQ-PPW  & 3.22 (0.57)   && 3.14 (0.48)  && 0.15 & 0.460 \\
  CFQ-PCW  & 3.01 (0.33)  && 2.92 (0.33)  && 0.29 & 0.137 \\
  CFQ-CONC  & 2.64 (1.73)  && 2.88 (1.68)   && 0.18  & 0.350\\
  CFQ-REST  & 3.14 (0.94)  && 3.24 (0.87)   && 0.12 & 0.563 \\
  CFQ-PE & 1.86 (0.77) && 2.24 (0.89) && 0.43 & 0.018* \\
  CFQ-MON  &  3.85 (0.95)  && 3.61 (0.89)  && 0.26  & 0.194 \\[1pt]
  \hline
  \multicolumn{7}{l}{LOC: loss of control; † p<0.10; *p<0.05} \\
  \multicolumn{7}{l}{a: Cohen's d} \\
  \multicolumn{7}{l}{b: p-values from independent samples t-tests} \\
\end{tabular}
\end{table}

\FloatBarrier

## Feeding Practices and Attitudes 

Parents of children who reported LOC-eating were less likely to report pressuring children to eat compared to parents of children with no LOC-eating (t(72) = -2.41, p = 0.018). No other feeding practices or attitudes differed on average between children who did and did not report LOC-eating (p’s > 0.286; Table 3).

# Characterization of LOC-Eating

```{r load_analyses, echo=FALSE, include=FALSE}
source('LOC_ARM_Analyses.R')
```

## Association Rules Mining: Single Antecedent Attribute (Step 1)

The first step identified 29 rules with one attribute each. There were 19 rules pruned due to $\kappa$ < 0.20. The remaining 10 rules had $\kappa$ that ranged from 0.21 – 0.31 indicating fair agreement.

```{r LOCyes_step1, echo=FALSE, results='asis'}
kable(DataFrame_pruned.rules_lhs1_conf33[c(1,3:5, 7:10,14:15)], "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC-Single Predictors") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")) %>%
  landscape()
```

```{r LOCyes_step1tab2, echo=FALSE, results='asis'}
kable(xtabs_pruned.rules_lhs1_conf33, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC-Cross Tab of Single Predictors")
```
\FloatBarrier

## Association Rules Mining: Two Antecedent Attributes (Step 2) 

In the second step, 48 rules with two attributes were identified. All 48 rules had $\kappa$ > 0.20 (range: 0.27 – 0.41), indicating fair to moderate agreement. Additionally, all rules were significant after controlling for multiple comparisons. 

```{r LOCyes_step2_all, echo=FALSE, results='asis'}
kable(DataFrame_pruned.rules_lhs2_conf50_nosubset[c(1:2,4:6, 8:11, 15:18)], "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC-Multiple Predictors") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")) %>%
  landscape()
```

\FloatBarrier
Almost half the rules (n = 21) paired a child appetitive behavior with a parental feeding behavior while just over a third of rules (n = 17) paired two appetitive behaviors together. Less common were rules that paired two parental feeding practices together (n = 5, 10%), rules that included a family/parent characteristic (i.e., maternal weight status; n = 1, 2%), or rules that included a child demographic characteristic (i.e., Age 7-9 years; n = 3, 6%).
\FloatBarrier

```{r LOCyes_step2_allcat, echo=FALSE, results='asis'}
kable(xtabs_pruned.rules_lhs2_conf50_nosubset, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC-Cross tabs Multiple Predictors") %>%
  landscape()
```


## Clustering of Rules

The 48 rules identified in Step 2 were clustered using PAM, which resulted in four clusters (see Supplementary Materials for cluster metrics).

```{r LOCyes_step2_PlotGrid, echo=FALSE, include=TRUE}
pruned.rules_lhs2_conf50_nclustPlotGrid
```

```{r LOCyes_step2_Vsum_tab, echo=FALSE, results='asis'}
kable(pruned.rules_lhs2_conf50_nclust_Vsum, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC-Cluster Metrics") 
```

\FloatBarrier

Average Silhouette Widths
```{r LOCyes_step2_clust5_silplot, echo=FALSE, include=TRUE}
plot(silhouette(pruned.rules_lhs2_conf50_4clust), col = 2:3)
```
\FloatBarrier

Cluster Plot
```{r LOCyes_step2_clust5_clusplot, echo=FALSE, include=TRUE}
clusplot(pruned.rules_lhs2_conf50_4clust, main = "Cluster plot, k = 2", 
         color = TRUE)
```
\FloatBarrier

### Cluster 1

```{r LOCyes_clust4.1_xtab, echo=FALSE,  results='asis'}
kable(xtabs_pruned.rules_lhs2_conf50_nosubset_clust4.1, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC-Cluster 1") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

```{r LOCyes_clust4.1_qfreq, echo=FALSE,  results='asis'}
kable(qfreq_pruned.rules_lhs2_conf50_nosubset_clust4.1, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC-Cluster 1 Question Frequency") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

### Cluster 2

```{r LOCyes_clust4.2_xtab, echo=FALSE,  results='asis'}
kable(xtabs_pruned.rules_lhs2_conf50_nosubset_clust4.2, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC-Cluster 2 Question Frequency") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

```{r LOCyes_clust4.2_qfreq, echo=FALSE,  results='asis'}
kable(qfreq_pruned.rules_lhs2_conf50_nosubset_clust4.2, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC-Cluster 2 Question Frequency") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

### Cluster 3

```{r LOCyes_clust4.3_xtab, echo=FALSE,  results='asis'}
kable(xtabs_pruned.rules_lhs2_conf50_nosubset_clust4.3, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC-Cluster 3") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

```{r LOCyes_clust4.3_qfreq, echo=FALSE,  results='asis'}
kable(qfreq_pruned.rules_lhs2_conf50_nosubset_clust4.3, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC-Cluster 3 Question Frequency") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

### Cluster 4

```{r LOCyes_clust4.4_xtab, echo=FALSE,  results='asis'}
kable(xtabs_pruned.rules_lhs2_conf50_nosubset_clust4.4, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC-Cluster 4") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

```{r LOCyes_clust4.4_qfreq, echo=FALSE,  results='asis'}
kable(qfreq_pruned.rules_lhs2_conf50_nosubset_clust4.4, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC-Cluster 4 Question Frequency") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

## Testing Multiplicative Effects

To test for possible multiplicative effects, rules were limited to those that contained at least one of the attributes that individually characterized children with LOC-eating in step 1 (Table 4). This resulted in 39 rules, however, only nine rules had odds ratios that exceeded the 95% confidence intervals for the odds ratios from single attributes (Table S1). 

```{r LOCyes_step2_subsettab, echo=FALSE, results='asis'}
kable(DataFrame_pruned.rules_lhs2_conf50_lhs1_holm_sigtrend[c(1:2, 11:17)], "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC-Significant Additive") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")) %>%
  landscape()
```
\FloatBarrier


### CEBQ 7

 <!-- CEBQ 7 > Sometimes (FF) -->
```{r LOCyes_CEBQ7, echo=FALSE, results='asis'}
kable(CEBQ7_tab, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC: CEBQ 7 > Sometimes (FF)") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")) 
```
\FloatBarrier

 <!-- CEBQ 7 > Sometimes (FF) + CEBQ 1 > Sometimes (EF) -->
```{r LOCyes_CEBQ7.CEBQ1, echo=FALSE, results='asis'}
kable(CEBQ7.CEBQ1_tab, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC: CEBQ 7 > Sometimes (FF) + CEBQ 1 > Sometimes (EF)") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")) 
```
\FloatBarrier

<!-- CEBQ 7 > Sometimes (FF) + CFQ 28 < Neutral (PE) -->
```{r LOCyes_CEBQ7.CFQ28, echo=FALSE, results='asis'}
kable(CEBQ7.CFQ28_tab, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC: CEBQ 7 > Sometimes (FF) + CFQ 28 < Neutral (PE)") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")) 
```
\FloatBarrier

### CEBQ 33

<!-- CEBQ 33 > Sometimes (FF) -->
```{r LOCyes_CEBQ33, echo=FALSE, results='asis'}
kable(CEBQ33_tab, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC: CEBQ 33 > Sometimes (FF)") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")) 
```
\FloatBarrier

<!-- CEBQ 33 > Sometimes (FF) + Breastfeeding < 7 mo -->
```{r LOCyes_CEBQ33.BFls7mo, echo=FALSE, results='asis'}
kable(CEBQ33.BFls7mo_tab, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC: CEBQ 33 > Sometimes (FF) + Breastfeeding < 7 mo") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")) 
```
\FloatBarrier

<!-- CEBQ 33 > Sometimes (FF) + CEBQ 1 > Sometimes (EF) -->
```{r LOCyes_CEBQ33.CEBQ1, echo=FALSE, results='asis'}
kable(CEBQ33.CEBQ1_tab, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC: CEBQ 33 > Sometimes (FF) + CEBQ 1 > Sometimes (EF)") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")) 
```
\FloatBarrier

<!-- CEBQ 33 > Sometimes (FF) + CFQ 28 = Disagree (PE) -->
```{r LOCyes_CFQ28.CEBQ33, echo=FALSE, results='asis'}
kable(CFQ28.CEBQ33_tab, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC: CEBQ 33 > Sometimes (FF) + CFQ 28 = Disagree (PE)") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

### CEBQ 34

<!-- CEBQ 34 > Rarely (FR) -->
```{r LOCyes_CEBQ34, echo=FALSE, results='asis'}
kable(CEBQ34_tab, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC: CEBQ 34 > Rarely (FR)") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")) 
```
\FloatBarrier

<!-- CEBQ 34 > Rarely (FR) + CFQ 27 < Neutral (PE) -->
```{r LOCyes_CEBQ34.CFQ27, echo=FALSE, results='asis'}
kable(CEBQ34.CFQ27_tab, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC: CEBQ 34 > Rarely (FR) + CFQ 27 < Neutral (PE)") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")) 
```

\FloatBarrier

<!-- CEBQ 34 > Rarely (FR) + CFQ 28 = Dissagree (PE) -->
```{r LOCyes_CEBQ34.CFQ28, echo=FALSE, results='asis'}
kable(CEBQ34.CFQ28_tab, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC: CEBQ 34 > Rarely (FR) + CFQ 28 = Dissagree (PE)") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")) 
```
\FloatBarrier

### CFQ 20 

<!-- CFQ 20 = Agree (Restrict) -->
```{r LOCyes_CFQ20, echo=FALSE, results='asis'}
kable(CFQ20_tab, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC: CFQ 21 = Agree (Restrict)") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")) 
```
\FloatBarrier

<!-- CFQ 20 = Agree (Restrict) + CFQ 21 < Neutral (Restrict) -->
```{r LOCyes_CFQ20.CFQ21, echo=FALSE, results='asis'}
kable(CFQ20.CFQ21_tab, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC: CFQ 21 = Agree (Restrict) + CFQ 21 < Neutral (Restrict)") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")) 
```
\FloatBarrier

### CFQ 26

<!-- CFQ 26 = Dissagree (PE) -->
```{r LOCyes_CFQ26, echo=FALSE, results='asis'}
kable(CFQ26_tab, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC: CFQ 26 = Dissagree (PE)") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")) 
```
\FloatBarrier

<!-- CFQ 26 = Dissagree (PE) + CEBQ 12 > Rarely (FR) -->
```{r LOCyes_CEBQ12.CFQ26, echo=FALSE, results='asis'}
kable(CEBQ12.CFQ26_tab, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of LOC: CFQ 26 = Dissagree (PE) + CEBQ 12 > Rarely (FR))") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")) 
```
\FloatBarrier

# Characterization of Absence of LOC-Eating

## Association Rules Mining: Single Antecedent Attribute (Step 1)

The first step identified 107 rules with one attribute, only one of which had $\kappa$ > 0.20 ($\kappa$ = 0.28) indicating this rule had fair to moderate agreement. This individual rule was also significant (p = 0.001). 

```{r LOCno_step1, echo=FALSE, results='asis'}
kable(DataFrame_pruned.rules_lhs1_conf33_no_sig[c(1,3:5, 7:10, 14:15)], "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of No LOC-Single Predictors") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")) %>%
  landscape()
```


\FloatBarrier

## Association Rules Mining: Multiple Antecedent Attributes (Step 2)

In the second step, 1335 rules with two antecedents were identified, 11 of which had $\kappa$ > 0.20 ($\kappa$ = 0.21 – 0.28), indicating all rules had fair agreement. All 11 rules remained significant after controlling for multiple comparisons (Table 8). 

```{r LOCno_step2, echo=FALSE, results='asis'}
kable(DataFrame_pruned.rules_lhs2_conf50_no_nosubset[c(1:2,4:6, 8:11, 15:17)], "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of No LOC-Multiple Predictors") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")) %>%
  landscape()
```

Category frequencies for uncorrected rules
```{r LOCno_step2_cattab, echo=FALSE, results='asis'}
kable(xtabs_pruned.rules_lhs2_conf50_no_nosubset, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of No LOC-Cross Tab Mulitple Predictors") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

## Clustering of Rules

The 11 significant rules were clustered using PAM, which resulted in 2 clusters (see Supplemental Materials)

Plot of cluster metrics
```{r LOCno_step2_PlotGrid, echo=FALSE, include=TRUE}
pruned.rules_lhs2_conf50_no_nclustPlotGrid
```

Cluster Metrics
```{r LOCno_step2_Vsum_tab, echo=FALSE, results='asis'}
kable(pruned.rules_lhs2_conf50_no_nclust_Vsum, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of No LOC-Cluster Metrics") 
```

```{r LOCno_step2_clust4, echo=FALSE, results='asis'}
kable(xtabsClust_pruned.rules_lhs2_conf50_no_nosubset, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of NO LOC-Clusters")
```
\FloatBarrier

Average Silhouette Widths
```{r LOCno_step2_clust2_silplot, echo=FALSE, include=TRUE}
plot(silhouette(pruned.rules_lhs2_conf50_no_2clust), col = 2:3)
```
\FloatBarrier

Cluster Plot
```{r LOCno_step2_clust2_clusplot, echo=FALSE, include=TRUE}
clusplot(pruned.rules_lhs2_conf50_no_2clust, main = "Cluster plot, k = 3",
        color = TRUE)
```
\FloatBarrier

### Cluster 1

```{r LOCno_clust2.1_xtab, echo=FALSE,  results='asis'}
kable(xtabs_pruned.rules_lhs2_conf50_no_nosubset_clust2.1, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of NO LOC-Cluster 1") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

```{r LOCno_clust2.1_qfreq, echo=FALSE,  results='asis'}
kable(qfreq_pruned.rules_lhs2_conf50_no_nosubset_clust2.1_LHS1, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of NO LOC-Cluster 1 Question Frequency") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

### Cluster 2

```{r LOCno_clust2.2_xtab, echo=FALSE,  results='asis'}
kable(xtabs_pruned.rules_lhs2_conf50_no_nosubset_clust2.2, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of NO LOC-Cluster 2") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

```{r LOCno_clust2.2_qfreq, echo=FALSE,  results='asis'}
kable(qfreq_pruned.rules_lhs2_conf50_no_nosubset_clust2.2_LHS1, "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of NO LOC-Cluster 2 Question Frequency") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
\clearpage

## Testing Multiplicative Effects

All 11 rules contained the significant attribute from step 1 (CEBQ34 < ‘Sometimes’), however, none of the rules with two attributes had odds ratios that exceeded the 95% confidence interval for the odds ratio from the single attribute rule (Table S1). 

```{r LOCno_step2_subset, echo=FALSE, results='asis'}
kable(DataFrame_pruned.rules_lhs1_lhs2_conf50_no_lhs1_holm_sig[c(1:2, 11:19)], "latex", booktabs = TRUE, longtable = TRUE, digits = 3, caption = "Determinants of No LOC-Additive Effect OR Comparisons") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header")) %>%
  landscape()
```
\FloatBarrier

\clearpage
